### 2014-02-12 Beacon P3 Proposal/main.tex
Removed some verticle space to make it fit on 2 pages.
Minor word fixes to the BEACON proposal.

P3 is currently limited to evolving discrete value encoded linear
genomes which also limits the range of problems the approach can address.
We therefore also propose to examine ways to expand P3 into the
Genetic Programming area. We plan to leverage Grammatical Evolution~\cite{oneill:2001:grammatical}
to give P3 the ability to evolve programs.  Grammatical Evolution (GE) is a subset
of Genetic Programming which utilizes a non-trivial genotype to phenotype mapping, converting
binary strings into full fledged programs.  To apply GE, a domain expert first creates a
grammar which defines the structure of all possible useful programs.  When evaluating a
solution, bits are read from the individual to determine which grammar expansion rules to perform,
deterministically creating a program.  This is an ideal transition for
P3 since GE applications will be appear as binary string
applications requiring 
only modificiation to the evaluation step.

\subsubsection*{Intellectual Merit}
%Proposed work is highly innovative and has potential for having a ground-breaking impact in its field
%Project aligns with BEACON mission and shows promise of opening new areas for multidisciplinary investigation
%Project appears very likely to generate successful (funded) proposals
%Degree of Multidisciplinarity of Project - No chance

All previous parameter-less methods in evolutionary computing perform at least a constant factor
worse than when using methods with optimal problem specific parameter tuning~\cite{pelikan:2004:parameterlesshboa}.
What makes P3 so interesting as that in all of our preliminary data it has performed at
least a constant factor \textbf{better} than optimally tuned state-of-the-art algorithms.
However, these results are limited to artificial problems.  In order to perform a complete analysis,
P3 needs to be applied to real world optimization problems.  Through X-TOOLSS and 
with the help of engineers at NASA, this
analysis can be performed with relative ease.

@@

\subsubsection*{Broader Impacts}
%Education - Not likely
%Project is organized around solution of a problem identified by a particular company/group of companies as important to them
%Some diversity reflected among project participants (current or named for future appointment under project)
%Project participants are from two or more BEACON institutions
Once P3 has been integrated into X-TOOLSS, its parameter-less nature will allow
end users (specifically NASA engineers) to try P3 on their optimization problems with ease.
Our preliminary results suggest P3 will produce better quality solutions in less time
than existing X-TOOLSS optimizers.

>>>>

P3 is designed to evolve discrete value encoded linear
genomes which limits the range of problems this approach can address.
We therefore also propose to examine ways to expand P3 into the
Genetic Programming area. We plan to leverage Grammatical Evolution~\cite{oneill:2001:grammatical}
to give P3 the ability to evolve programs.  Grammatical Evolution (GE) is a subset
of Genetic Programming which utilizes a non-trivial genotype to phenotype mapping, converting
binary strings into full fledged programs.  To apply GE, a domain expert first creates a
grammar which defines the structure of all possible useful programs.  When evaluating a
solution, bits are read from the individual to determine which grammar expansion rules to perform,
deterministically creating a program.  This is an ideal transition for
P3 since GE applications will be appear as binary string
applications requiring 
only modificiation to the evaluation step.

\vspace{-2.5mm}
\subsubsection*{Intellectual Merit}
%Proposed work is highly innovative and has potential for having a ground-breaking impact in its field
%Project aligns with BEACON mission and shows promise of opening new areas for multidisciplinary investigation
%Project appears very likely to generate successful (funded) proposals
%Degree of Multidisciplinarity of Project - No chance

All previous parameter-less methods in evolutionary computing perform at least a constant factor
worse than when using methods with optimal problem specific parameter tuning~\cite{pelikan:2004:parameterlesshboa}.
What makes P3 so interesting is that in all of our preliminary data it has performed at
least a constant factor \textbf{better} than optimally tuned state-of-the-art algorithms.
However, these results are limited to artificial problems.  In order to perform a complete analysis,
P3 needs to be applied to real world optimization problems.  Through X-TOOLSS and 
with the help of engineers at NASA, this
analysis can be performed with relative ease.

@@

\vspace{-2.5mm}
\subsubsection*{Broader Impacts}
%Education - Not likely
%Project is organized around solution of a problem identified by a particular company/group of companies as important to them
%Some diversity reflected among project participants (current or named for future appointment under project)
%Project participants are from two or more BEACON institutions
Once P3 has been integrated into X-TOOLSS, its parameter-less nature will allow
end users (specifically NASA engineers) to try P3 on their optimization problems with ease.
Our preliminary results suggest P3 will produce better quality solutions in less time
than existing X-TOOLSS optimizers.
